---
title: "Remote sensing for precision agriculture"
output: 
 flexdashboard::flex_dashboard:
    theme: readable
    social: menu
    logo: Picture11.png
    favicon: Picture11.png
    orientation: rows
    # source_code: embed
runtime: shiny
---

```{r global, include=FALSE}
# load data in 'global' chunk so it can be shared by all users of the dashboard
library(ggplot2)
library(mgcv)
library(shiny)
library(shinythemes)
library(plotly)
library(hsdar)  # Required for PROSPECT and PROSAIL functions
```

PROSAIL Model
=====================================

Inputs {.sidebar}
-----------------------------------------------------------------------
#### Leaf parameters
```{r}
sliderInput("N", label = "Leaf Mesophyll index (N)", min = 1, value = c(1.2,1.5), max = 2.5, step = .1, animate = animationOptions(interval = 1000, loop = T))
sliderInput("Cm", label = "Dry matter content (Cm, g cm-2)",  min = 0, value = c(0.01,0.012), max = 0.02, step = .001 )
sliderInput("Cw", label = "Equivalent water thickness \n(Cw, g cm-2) ", min = 0, value = c(0.02, 0.03), max = 0.05 , step = .01 )
sliderInput("Cab", label = "Leaf Chlorophyll Content (Cab, ┬Ąg cm-2)", min = 0, value = c(45,60) , max = 90,  step = 5, animate = animationOptions(interval = 1000, loop = T))
```

#### Canopy parameters
```{r}
sliderInput( "LAI", label = "Leaf Area Index (LAI, m\u00b2 / m\u00b2)",
                                  min = 1, max = 10, step = .5,
                                  value =  c(1, 2),
                                  animate = animationOptions(interval = 1000, loop = T))
sliderInput("lidfa", label = "Average Leaf Angle (ALA, gradi ┬░)",  min = 0, value = c(45,67), max = 90, step = .5)
```

##### Satellite
```{r}
selectInput("sensor", label = "Choose a sensor: ",
            choices = c("Sentinel2a", "Sentinel2b", "Landsat4", "Landsat5", "Landsat7", "Landsat8", "Quickbird", "RapidEye", "WorldView2-4", "WorldView2-8"),
            selected = "Sentinel2a")
```

##### Vegetation indices
```{r}
selectInput("vis", label = "Choose a VIs: ",
choices = c("NDVI", "NDRE", "GNDVI"), selected = "NDVI")
```

Outputs 
-----------------------------------------------------------------------

### Leaf reflectance - PROSPECT
```{r }
dataset <- reactive({
  tryCatch({
    spectra <- hsdar::PROSPECT(parameterList = expand.grid(
      N = input$N, 
      Cm = input$Cm, 
      Cw = input$Cw, 
      Cab = input$Cab
    ))
    prospectfile <- data.frame(Wav = 400:2500, Reflectance = t(spectra@spectra@spectra_ma))
    Reflectance <- apply(prospectfile[, 2:ncol(prospectfile)], 1, mean)
    Reflectance.sd <- apply(prospectfile[, 2:ncol(prospectfile)], 1, sd)
    data.frame(Wav = 400:2500, mean = round(Reflectance, 3), sd = round(Reflectance.sd, 3))
  }, error = function(e) {
    data.frame(Wav = 400:2500, mean = 0, sd = 0)
  })
})

renderPlotly({
  p1 <- ggplot(dataset(),aes(x=Wav,y=mean)) + geom_line(colour='darkgreen', lty="dashed", lwd=1.2) +
            geom_ribbon(aes(ymin=mean-sd, ymax=mean+sd, x=Wav), alpha = 0.3,  fill="green") +
            theme_classic(base_size = 14) +
            labs(x="Wavelength (nm)", y = "Reflectance (-)") +
            scale_x_continuous(limits = c(400, 2500)) + scale_y_continuous(limits = c(0, 1))
  
 ggplotly(p1)
})
```

### Canopy reflectance - SAIL  
```{r }
# Optimized: compute PROSAIL once and reuse
prosail_spectra <- reactive({
  tryCatch({
    hsdar::PROSAIL(parameterList = expand.grid(
      N = input$N, 
      Cm = input$Cm, 
      Cw = input$Cw, 
      Cab = input$Cab,
      LAI = input$LAI, 
      TypeLidf = 2, 
      lidfa = input$lidfa
    ))
  }, error = function(e) {
    NULL
  })
})

dataset2 <- reactive({
  if (is.null(prosail_spectra())) return(data.frame(Wav = 400:2500, mean = 0, sd = 0))
  prosailfile <- data.frame(Wav = 400:2500, Reflectance = t(prosail_spectra()@spectra@spectra_ma))
  Reflectance <- apply(prosailfile[, 2:ncol(prosailfile)], 1, mean)
  Reflectance.sd <- apply(prosailfile[, 2:ncol(prosailfile)], 1, sd)
  data.frame(Wav = 400:2500, mean = round(Reflectance, 3), sd = round(Reflectance.sd, 3))
})

dataset_s2 <- reactive({
  if (is.null(prosail_spectra())) return(data.frame(Wav = numeric(0), mean = numeric(0), sd = numeric(0)))
  tryCatch({
    spectra.S2 <- hsdar::spectralResampling(prosail_spectra(), input$sensor)
    prosail.spectra.S2 <- spectra.S2@spectra@spectra_ma
    Reflectance.s2 <- apply(prosail.spectra.S2[, 1:ncol(prosail.spectra.S2)], 2, mean)
    Reflectance.s2.sd <- apply(prosail.spectra.S2[, 1:ncol(prosail.spectra.S2)], 2, sd)
    data.frame(Wav = spectra.S2@wavelength, mean = round(Reflectance.s2, 3), sd = round(Reflectance.s2.sd, 3))
  }, error = function(e) {
    data.frame(Wav = numeric(0), mean = numeric(0), sd = numeric(0))
  })
})

dataset_s2_show <- reactive({
  if (is.null(prosail_spectra())) return(data.frame())
  tryCatch({
    parameter <- expand.grid(
      N = input$N, 
      Cm = input$Cm, 
      Cw = input$Cw, 
      Cab = input$Cab,
      LAI = input$LAI, 
      TypeLidf = 2, 
      lidfa = input$lidfa
    )
    spectra.S2 <- hsdar::spectralResampling(prosail_spectra(), input$sensor)
    prosail.spectra.S2 <- data.frame(round(spectra.S2@spectra@spectra_ma, 4))
    prosail.spectra.S2 <- cbind(parameter, prosail.spectra.S2)
    colnames(prosail.spectra.S2)[8:ncol(prosail.spectra.S2)] <- paste0("R", spectra.S2@wavelength)
    colnames(prosail.spectra.S2)[7] <- "ALA"
    prosail.spectra.S2$TypeLidf <- NULL
    data.frame(prosail.spectra.S2)
  }, error = function(e) {
    data.frame()
  })
})
      
renderPlotly({ 
  p <- ggplot() +
    geom_line(data = dataset2(), aes(x = Wav, y = mean), colour = 'darkred', lty = "dashed", lwd = 1.2) +
    geom_ribbon(data = dataset2(), aes(ymin = mean - sd, ymax = mean + sd, x = Wav), fill = "red", alpha = 0.3) +
    geom_point(data = dataset_s2(), aes(x = Wav, y = mean), fill = "green", color = "black", pch = 21, size = 3, alpha = .33) +
    theme_classic(base_size = 14) +
    labs(x = "Wavelength (nm)", y = "Reflectance (-)") +
    scale_x_continuous(limits = c(400, 2500)) + 
    scale_y_continuous(limits = c(0, 1))
  ggplotly(p)
})
```

```{r include=FALSE}
x <- reactive({
  df <- dataset_s2_show()
  if (nrow(df) == 0) return(data.frame())
  colnames(df) <- c("N", "Cm", "Cw", "Cab", "LAI", "ALA", "B1", 
                    "B2", "B3", "B4", "B5", "B6", "B7", "B8", 
                    "B8a", "B9", "B10", "B11", "B12")
  df$NDVI <- (df$B8 - df$B4) / (df$B8 + df$B4)
  df$NDRE <- (df$B8 - df$B5) / (df$B8 + df$B5)
  df$GNDVI <- (df$B8 - df$B3) / (df$B8 + df$B3)
  return(df)
})
```
Outputs 
-----------------------------------------------------------------------

### LAI  
```{r}
renderPlotly({ 
  df <- x()
  if (nrow(df) == 0) return(plotly_empty())
  vi_col <- input$vis
  p <- ggplot(data = df, aes(x = .data[[vi_col]], y = LAI)) +
    geom_point(fill = "green", color = "black", pch = 21, size = 3, alpha = .33) +
    geom_smooth(method = lm, se = TRUE) +
    theme_classic(base_size = 14) +
    labs(x = input$vis, y = "LAI (m┬▓/m┬▓)")
  ggplotly(p)
})
```

### Chlorophyll
```{r}
renderPlotly({ 
  df <- x()
  if (nrow(df) == 0) return(plotly_empty())
  vi_col <- input$vis
  p <- ggplot(data = df, aes(x = .data[[vi_col]], y = Cab)) +
    geom_point(fill = "green", color = "black", pch = 21, size = 3, alpha = .33) +
    geom_smooth(method = lm, se = TRUE) +
    theme_classic(base_size = 14) +
    labs(x = input$vis, y = "Cab (┬Ąg cmŌü╗┬▓)")
  ggplotly(p)
})

Info
=====================================

Created by: UCSC Field Crops Group - Remote sensing team

**Michele Croci**, **Giorgio Impollonia** and **Stefano Amaducci**

